Novel Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering

### 2025-07-25 paper/main.tex
Finish first version

\documentclass{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{subfigure}
\usepackage{xcolor}
\usepackage{epstopdf}

@@

    \title{To Be Decided}
    \author{Andr\'e Costa Batista, Ricardo Adriano, and Lucas S. Batista
        \thanks{This work was supported in part by the Brazilian agency CAPES (Coordination for the Improvement of Higher Education Personnel) under Grant 88887.463864/2019-00, the scholarship FAPEMIG-CNPQ (process APQ-06716-24), and CNPq (The National Council for Scientific and Technological Development).}

        \thanks{A. C. Batista, R. Adriano, and L. S. Batista are with the Department of Electrical Engineering, Universidade Federal de Minas Gerais, Belo Horizonte, MG 31270-901, Brazil (e-mail: andre-costa@ufmg.br; rluiz@ufmg.br; lusoba@ufmg.br). A. C. Batista and L. S. Batista are also with Operations Research and Complex Systems Laboratory (ORCS Lab), Belo Horizonte, MG, Brazil.}}

@@

    \begin{abstract}
        To be written.
    \end{abstract}

    \begin{IEEEkeywords}
        Keyword 1, keyword 2, keyword 3. Remember: alphabetical order.
    \end{IEEEkeywords}

@@

        Specialized algorithms have been developed to address specific problem characteristics. These include the DORT method \cite{chen2018computational} for electromagnetic signal time reversal, MUSIC \cite{zhong2007music} for small scatterers, and Compressive Sensing \cite{massa2015compressive} for phaseless field data. For weak scatterer problems, effective approaches include First-Order Born Approximation, Backpropagation, and Rytov approximation \cite{chen2018computational}.

@@

        % Quais formas de avaliar soluções e quais ferramentas já existem (incluir aquele trabalho do Kurrant que é software para câncer de mama).

        % Em grande parte destes trabalhos, os algoritmos propostos são testados e avaliados em métricas como o mean square error (MSE) da estimativa do contraste pixel a pixel ou algo similar \cite{yin2023subspace,zhang2022023,salucci2022learned,wang2023push,liu2022som,bevacqua2021simple,bevacqua2021effective}. Este tipo de abordagem leva em consideração a precisão na estimativa do contraste na forma direta e, indiretamente, pode dar uma perspectiva de quão boa a reconstrução da posição e geometria dos objetos pode ser, uma vez que erros na geometria e posicionamento podem afetar nessa métrica. No entanto, uma geometria bem precisa com uma má estimativa do contraste pode resultar em um erro considerável neste tipo de métrica, por exemplo. Logo, aspectos comparar o desempenho no aspecto de quão bem a geometria e a posição dos objetos são recuperadas não são contemplados adequadamente por este tipo de métrica. Além disso, a métrica MSE não é adequada para avaliar algoritmos qualitativos, uma vez que estes não estimam o contraste do meio. Vale à pena destacar também a métrica Structural Similarity (SSIM) \cite{wang2004image} to quantitatively show the reconstruction visual quality, which is designed to compute the mismatch between reconstructed contrast results and corresponding GTs both on the pixel-wise level and perceptual level. Ao invés de fazer uma comparação pixel a pixel, a métrica leva em consideração aspectos de luminância, contraste e estrutura de uma imagem qualquer. Portanto, ao mesmo tempo que fornece uma quantificação mais profunda da qualidade de construção como um todo, ela não vai mensurar diretamente aspectos isolados como geometria e posição.

        In most of these studies, the proposed algorithms are tested and evaluated using metrics such as the mean square error (MSE) of pixel-by-pixel contrast estimation or similar approaches \cite{yin2023subspace,zhang2023iterative,salucci2022learned,wang2023push,liu2022som,bevacqua2021simple,bevacqua2021effective}. This type of approach directly considers the precision of contrast estimation and can indirectly provide perspective on how well the reconstruction of object position and geometry might be, since errors in geometry and positioning can affect this metric. However, a highly accurate geometry with poor contrast estimation can result in considerable error in this type of metric, for example. Therefore, aspects of comparing performance regarding how well object geometry and position are recovered are not adequately addressed by this type of metric. Furthermore, the MSE metric is not suitable for evaluating qualitative algorithms, since these do not estimate the medium's contrast.

@@

        Specifically for breast imaging, a set of metrics has been proposed in the literature that considers not only the precision in estimating electrical properties, but also the accuracy of the reconstructed tissue geometry \cite{kurrant2021evaluating}. Each geometry (original and reconstructed) is converted into vectors, and the metric is calculated using a formula that performs the dot product and norm of these vectors. To the best of the authors' knowledge, this is the only metric that can isolately consider the geometry aspect of the scatterer, even though it is designed specifically for breast imaging.

        % Descrever a lacuna para proposição de outros indicadores, tais como de posição e forma. Introduzir a minha proposta destacando vantagens, desvantagens e originalidade.

        % O objetivo deste trabalho é fornecer mais métricas para auxiliar na avaliação do desempenho de algoritmos. Com uma gama maior de indicadores pode ser possível ter uma visão mais abrangente sobre a capacidade dos algoritmos em diferentes cenários. Por isso, nossa contribuição se baseia na proposição de dois novos indicadores para avaliar o desempenho dos algoritmos na recuperação da geometria e posição dos espalhadores. O primeiro indicador quantifica o erro de forma, enquanto o segundo quantifica o erro de posição. A originalidade do trabalho reside no fato de que estes indicadores podem calcular de maneira mais isolada esses dois aspectos que são relevantes da descrição do desempenho de algoritmos para o problema inverso de espalhamento eletromagnético. Além disso, estes indicadores são projetados para serem aplicáveis a qualquer algoritmo que reconstrua a imagem, independentemente de estimar ou não o contraste.

@@

        % Organização do texto

@@

			The contrast function reconstructed by many algorithms -- such as BIM, DBIM, CSI, SOM, among others -- is commonly a discretized approximation of a continuous surface. Therefore, even if the original image contains only objects with well-defined boundaries and homogeneous contrast, the image of these objects obtained by the algorithms will have frequently smooth edges, i.e., the contrast value gradually varies between the background medium and the object's value. Consequently, identifying a contour in the resulting image is heuristic because it requires selecting a criterion to define the contrast value at which a pixel can be considered as belonging to the object. For simplicity, the threshold $T$ for considering a pixel in the recovered image to be within an object's contour will be defined as half of the total contrast variation in the image, i.e.:
			\begin{equation}
				T = \min(|\Xr|) + \frac{1}{2} \left[\max(|\Xr|)-\min(|\Xr|)\right]
			\end{equation}

@@

			This approach has advantages and disadvantages. If the reconstructed image contains multiple scatterers, and one or more of them has a contrast below this threshold, the methodology will fail to detect the contour of these objects. However, in scenarios where there is only one scatterer in the image, this approach is simple and effective. In fact, a single scatterer is the most objective way to test an algorithm's potential in recovering geometry, since the presence of multiple scatterers can degrade the algorithm's performance due to the influence of the induced currents in each scatterer on the scattering of the other. Furthermore, this approach poses no issues for algorithms capable of accurately capturing contours, such as machine learning-based methods. Moreover, instead of using the values from the original image, it is more beneficial to use only the values from the reconstructed image, both to isolate the influence of error in the contrast estimate and to apply the metric to qualitative methods that do not estimate contrast. If, for some reason, the original contrast function involves soft boundaries of the objects, the threshold might also be applied to the original image.

@@

            It should be noted that inaccuracies in the reconstructed geometry of objects can significantly influence the position error calculation. For example, if a star-shaped object with five points is reconstructed with one point distorted, this distortion will affect the object's centroid, thereby impacting the position error. However, this effect is expected, as any criterion for determining an object's position inherently considers the pixels defining it, as it is for its geometry. Furthermore, the proposed indicator is straightforward and versatile, applicable even in scenarios involving images with multiple objects. The Algorithm \ref{alg:compute_zeta_p} summarizes the steps for calculating the position error indicator.

@@

        The DOI dimensions were set to $2\lambda_b \times 2\lambda_b$, and all reconstructions were performed using a $40 \times 40$ pixel discretization.

@@

                \begin{figure*}[!htb]
                    \subfigure[Ground-Truth]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/0}}
                    \subfigure[LSM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/1}}
                    \subfigure[OSM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/2}} \\
                    \subfigure[BIM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/3}}
                    \subfigure[CSI]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/4}}
                    \subfigure[SOM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/5}}
                    \caption{Shape recovering study, single scatterer: ground-truth and reconstructed images by each algorithm.}
                    \label{fig:shape:single:recons}
                \end{figure*}

@@

                \begin{figure*}[!htb]
                    \centering
                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_0.eps}}
                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_1.eps}}
                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_2.eps}}
                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_3.eps}}
                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_4.eps}} \\
                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_0.eps}}
                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_1.eps}}
                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_2.eps}}
                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_3.eps}}
                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_4.eps}}
                    \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
                    \label{fig:shape:vary:recons}
                \end{figure*}

@@

                \begin{figure}[!htb]
                    \centering
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
                    \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
                    \label{fig:shape:vary:indicators}
                \end{figure}

@@

                \begin{figure}[!htb]
                    \centering
                    \subfigure[]{\includegraphics[width=.5\columnwidth]{./experiments/average/figs/dnl.eps}\label{fig:shape:average:dnl}} \\
                    \subfigure[]{\includegraphics[width=\columnwidth]{./experiments/average/figs/plot.eps}\label{fig:shape:average:zeta_s}}
                    \caption{Shape recovering study, average performance: (a) Degree of Nonlinearity (DNL) for each scatterer; (b) shape error indicator $\zeta_S$ for each algorithm in each instance.}
                    \label{fig:shape:average}   
                \end{figure}

@@

                \begin{figure}
                    \centering
                    \includegraphics[width=.8\columnwidth]{./experiments/average/figs/confidence_intervals.eps}
                    \caption{Shape recovering study, average performance: Confidence intervals (95\%) for the shape error indicator $\zeta_S$ for each pair of algorithms.}
                    \label{fig:shape:average:confidence_intervals}
                \end{figure}

@@

                \begin{figure*}[!htb]
                    \subfigure[Ground-Truth]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/0.eps}\label{fig:position:single:ground_truth}}
                    \subfigure[OSM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/1.eps}}
                    \subfigure[BIM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/2.eps}} \\
                    \subfigure[CSI]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/3.eps}}
                    \subfigure[SOM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/4.eps}}
                    \subfigure[CA]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/5.eps}}
                    \caption{Position detection study, single scatterer: ground-truth and reconstructed images by each algorithm.}
                    \label{fig:position:single:recons}
                \end{figure*}

@@

                \begin{figure*}[!htb]
                    \subfigure[Ground-Truth]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/0.eps}\label{fig:position:multiple:ground_truth}}
                    \subfigure[OSM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/1.eps}}
                    \subfigure[BIM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/2.eps}} \\
                    \subfigure[CSI]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/3.eps}}
                    \subfigure[SOM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/4.eps}}
                    \subfigure[CA]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/5.eps}}
                    \caption{Position detection study, multiple scatterer: ground-truth and reconstructed images by each algorithm.}
                    \label{fig:position:multiple:recons}
                \end{figure*}

@@

            Since the repository provides three-dimensional phantoms while our scattering model is two-dimensional, a representative cross-section focusing on the breast interior was extracted, as shown in Fig. \ref{fig:breast:phantom:ground_truth}. The resulting image contains 328 $\times$ 212 pixels with a spatial resolution of 0.5 mm $\times$ 0.5 mm per pixel.

            The phantom includes four tissue types: fatty, transitional, fibroglandular, and skin. The breast is immersed in a homogeneous background medium with relative permittivity $\epsilon_{rb} = 10$ and conductivity $\sigma = 0$ S/m. The operating frequency was set to 1 GHz, with electrical properties of breast tissues determined using the Debye model.

            The experimental configuration follows the previous studies: 80 incident sources, 80 measurement points, and 5\% noise level. Under these conditions, the DNL for this experiment is 0.05. Since the interior of the breast is a complex structure, keeping a low DNL value is an important strategy to facilitate the reconstruction.

            The algorithm parameters were readjusted as follows:
            \begin{itemize}
                \item Linear Sampling Method (LSM):
                \begin{itemize}
                    \item Threshold: 0.7;
                    \item Regularization Method: Conjugate Gradient with 300 iterations.
                \end{itemize}
                \item Orthogonality Sampling Method (OSM):
                \begin{itemize}
                    \item Threshold: 0.35;
                \end{itemize}
                \item Born Iterative Method (BIM):
                \begin{itemize}
                    \item Regularization Method: Conjugate Gradient with 300 iterations.
                    \item Stopping Criterion: 30 iterations.
                \end{itemize}
                \item Contrast Source Inversion (CSI):
                \begin{itemize}
                    \item Stopping Criterion: 300 iterations.
                \end{itemize}
                \item Subspace Optimization Method (SOM):
                \begin{itemize}
                    \item Stopping Criterion: 30 iterations.
                    \item Eigenvalue Cutoff Index: 5.
                \end{itemize}
            \end{itemize}

@@

% Figure example.
\begin{figure}[!t]
    \centerline{\includegraphics[width=\columnwidth]{fig1.png}}
    \caption{Magnetization as a function of applied field. It is good practice to explain the significance of the figure in the caption.}
    \label{example}
\end{figure}

>>>>

\documentclass{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{subfigure}
\usepackage{xcolor}
\usepackage{epstopdf}
\usepackage{url}

@@

    \title{Novel Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering}
    \author{Andr\'e Costa Batista, Ricardo Adriano, and Lucas S. Batista
    \thanks{This work was supported in part by the Brazilian agency CAPES (Coordination for the Improvement of Higher Education Personnel) under Grant 88887.463864/2019-00, the scholarship FAPEMIG-CNPQ (process APQ-06716-24), and CNPq (The National Council for Scientific and Technological Development).}
    \thanks{A. C. Batista, R. Adriano, and L. S. Batista are with the Department of Electrical Engineering, Universidade Federal de Minas Gerais, Belo Horizonte, MG 31270-901, Brazil (e-mail: andre-costa@ufmg.br; rluiz@ufmg.br; lusoba@ufmg.br). A. C. Batista and L. S. Batista are also with Operations Research and Complex Systems Laboratory (ORCS Lab), Belo Horizonte, MG, Brazil.}}

@@

    \begin{abstract}
        Microwave imaging is a low-cost, non-invasive technique for detecting and characterizing objects in inaccessible media through electromagnetic field measurements. The evaluation of algorithms that solve the related electromagnetic inverse scattering problem typically relies on metrics such as Mean Square Error (MSE) or Structural Similarity (SSIM), which primarily assess contrast estimation accuracy but provide limited insight into the recovery of object geometry and position. This paper introduces two novel performance indicators specifically designed to evaluate electromagnetic inverse scattering algorithms: a shape error indicator that quantifies geometric reconstruction accuracy, and a position error indicator that measures object localization precision. The proposed indicators are applicable to both qualitative and quantitative methods, even when they are combined in an experiment. Comprehensive experimental validation is conducted using traditional algorithms: Linear Sampling Method (LSM), Orthogonality Sampling Method (OSM), Born Iterative Method (BIM), Contrast Source Iterative Method (CSI), Subspace Optimization Method (SOM), and Circle Approximation (CA). Three distinct experimental frameworks are employed: shape recovery studies, position detection studies, and a realistic breast phantom study demonstrating their applicability. Supported by robust statistical analysis, the experiments revealed that: (a) in scenarios with a single scatterer and low Degree of Nonlinearity, BIM achieves the best average performance in object geometry recovery; and (b) in scenarios with a single small-sized, high-contrast scatterer, SOM and OSM achieve the best average performance in target localization. These indicators provide useful tools for algorithm development, benchmarking studies, and performance assessment in electromagnetic inverse scattering applications.
    \end{abstract}

    \begin{IEEEkeywords}
        Algorithm evaluation, electromagnetic inverse scattering, microwave imaging, performance indicators.
    \end{IEEEkeywords}

@@

        Specialized algorithms have been developed to address specific problem characteristics. These include the DORT method (Decomposition of the Time-Reversal Operator) \cite{chen2018computational} for electromagnetic signal time reversal, Multiple Signal Classification (MUSIC) \cite{zhong2007music} for small scatterers, and Compressive Sensing \cite{massa2015compressive} for phaseless field data. For weak scatterer problems, effective approaches include First-Order Born Approximation, Backpropagation, and Rytov approximation \cite{chen2018computational}.

@@

        In most of these studies, the proposed algorithms are tested and evaluated using metrics such as the Mean Square Error (MSE) of pixel-by-pixel contrast estimation or similar approaches \cite{yin2023subspace,zhang2023iterative,salucci2022learned,wang2023push,liu2022som,bevacqua2021simple,bevacqua2021effective}. This type of approach directly considers the precision of contrast estimation and can indirectly provide perspective on how well the reconstruction of object position and geometry might be, since errors in geometry and positioning can affect this metric. However, a highly accurate geometry with poor contrast estimation can result in considerable error in this type of metric, for example. Therefore, aspects of comparing performance regarding how well object geometry and position are recovered are not adequately addressed by this type of metric. Furthermore, the MSE metric is not suitable for evaluating qualitative algorithms, since these do not estimate the medium's contrast.

@@

        Specifically for breast imaging, a set of metrics has been proposed in the literature that considers not only the precision in estimating electrical properties, but also the accuracy of the reconstructed tissue geometry \cite{kurrant2021evaluating}. Each geometry (original and reconstructed) is converted into vectors, and the metric is calculated using a formula that performs the dot product and norm of these vectors. To the best of the authors' knowledge, this is the only metric that can independently consider the geometry aspect of the scatterer, even though it is designed specifically for breast imaging.

@@

@@

			The contrast function reconstructed by many algorithms -- such as BIM, DBIM, CSI, SOM, among others -- is commonly a discretized approximation of a continuous surface. Therefore, even if the original image contains only objects with well-defined boundaries and homogeneous contrast, the image of these objects obtained by the algorithms will frequently have smooth edges, i.e., the contrast value gradually varies between the background medium and the object's value. Consequently, identifying a contour in the resulting image is heuristic because it requires selecting a criterion to define the contrast value at which a pixel can be considered as belonging to the object. For simplicity, the threshold $T$ for considering a pixel in the recovered image to be within an object's contour will be defined as half of the total contrast variation in the image, i.e.:
			\begin{equation}
				T = \min(|\Xr|) + \frac{1}{2} \left[\max(|\Xr|)-\min(|\Xr|)\right]
			\end{equation}

@@

            This approach has advantages and disadvantages. If the reconstructed image contains multiple scatterers, and one or more of them has a contrast below this threshold, the methodology will fail to detect the contour of these objects. However, in scenarios where there is only one scatterer in the image, this approach is simple and effective. In fact, a single scatterer is the most objective way to test an algorithm's potential in recovering geometry, since the presence of multiple scatterers can degrade the algorithm's performance due to the influence of the induced currents in each scatterer on the scattering of the others. Furthermore, this approach poses no issues for algorithms capable of accurately capturing contours, such as machine learning-based methods. Moreover, instead of using the values from the original image, it is more beneficial to use only the values from the reconstructed image, both to isolate the influence of error in the contrast estimate and to apply the metric to qualitative methods that do not estimate contrast. If, for some reason, the original contrast function involves soft boundaries of the objects, the threshold might also be applied to the original image.

@@

            It should be noted that inaccuracies in the reconstructed geometry of objects can significantly influence the position error calculation. For example, if a star-shaped object with five points is reconstructed with one point distorted, this distortion will affect the object's centroid, thereby impacting the position error. However, this effect is expected, as any criterion for determining an object's position inherently considers the pixels defining it, just as it does for its geometry. Furthermore, the proposed indicator is straightforward and versatile, applicable even in scenarios involving images with multiple objects. The Algorithm \ref{alg:compute_zeta_p} summarizes the steps for calculating the position error indicator.

@@

        The DOI dimensions were set to $2\lambda_b \times 2\lambda_b$, and all reconstructions were performed using a $40 \times 40$ pixel discretization. All implementations necessary for this work are available in the repository at \url{https://github.com/andre-batista/NPISPAEIS} for reproducibility purposes.

@@

                \begin{figure*}[!htb]
                    \centering
                    \subfigure[Ground-Truth]{\includegraphics[width=0.3\textwidth]{./experiments/shape/star/figs/0.eps}}
                    \subfigure[LSM]{\includegraphics[width=0.3\textwidth]{./experiments/shape/star/figs/1.eps}}
                    \subfigure[OSM]{\includegraphics[width=0.3\textwidth]{./experiments/shape/star/figs/2.eps}} \\
                    \subfigure[BIM]{\includegraphics[width=0.3\textwidth]{./experiments/shape/star/figs/3.eps}}
                    \subfigure[CSI]{\includegraphics[width=0.3\textwidth]{./experiments/shape/star/figs/4.eps}}
                    \subfigure[SOM]{\includegraphics[width=0.3\textwidth]{./experiments/shape/star/figs/5.eps}}
                    \caption{Shape recovering study, single scatterer: ground-truth and reconstructed images by each algorithm.}
                    \label{fig:shape:single:recons}
                \end{figure*}

@@

                \begin{figure*}[!htb]
                    \centering
                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{./experiments/shape/vary/figs/osm_0.eps}}
                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{./experiments/shape/vary/figs/osm_1.eps}}
                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{./experiments/shape/vary/figs/osm_2.eps}}
                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{./experiments/shape/vary/figs/osm_3.eps}}
                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{./experiments/shape/vary/figs/osm_4.eps}} \\
                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{./experiments/shape/vary/figs/som_0.eps}}
                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{./experiments/shape/vary/figs/som_1.eps}}
                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{./experiments/shape/vary/figs/som_2.eps}}
                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{./experiments/shape/vary/figs/som_3.eps}}
                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{./experiments/shape/vary/figs/som_4.eps}}
                    \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
                    \label{fig:shape:vary:recons}
                \end{figure*}

@@

                \begin{figure}[!htb]
                    \centering
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/shape/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/shape/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
                    \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
                    \label{fig:shape:vary:indicators}
                \end{figure}

@@

                \begin{figure}[!htb]
                    \centering
                    \subfigure[]{\includegraphics[width=.5\columnwidth]{./experiments/shape/average/figs/dnl.eps}\label{fig:shape:average:dnl}} \\
                    \subfigure[]{\includegraphics[width=\columnwidth]{./experiments/shape/average/figs/plot.eps}\label{fig:shape:average:zeta_s}}
                    \caption{Shape recovering study, average performance: (a) Degree of Nonlinearity (DNL) for each scatterer; (b) shape error indicator $\zeta_S$ for each algorithm in each instance.}
                    \label{fig:shape:average}   
                \end{figure}

@@

                \begin{figure}
                    \centering
                    \includegraphics[width=.8\columnwidth]{./experiments/shape/average/figs/confidence_intervals.eps}
                    \caption{Shape recovering study, average performance: Confidence intervals (95\%) for the shape error indicator $\zeta_S$ for each pair of algorithms.}
                    \label{fig:shape:average:confidence_intervals}
                \end{figure}

@@

                \begin{figure*}[!htb]
                    \centering
                    \subfigure[Ground-Truth]{\includegraphics[height=0.5\columnwidth]{../experiments/position/single/figs/0.eps}\label{fig:position:single:ground_truth}}
                    \subfigure[OSM]{\includegraphics[height=0.5\columnwidth]{../experiments/position/single/figs/1.eps}}
                    \subfigure[BIM]{\includegraphics[height=0.5\columnwidth]{../experiments/position/single/figs/2.eps}} \\
                    \subfigure[CSI]{\includegraphics[height=0.5\columnwidth]{../experiments/position/single/figs/3.eps}}
                    \subfigure[SOM]{\includegraphics[height=0.5\columnwidth]{../experiments/position/single/figs/4.eps}}
                    \subfigure[CA]{\includegraphics[height=0.5\columnwidth]{../experiments/position/single/figs/5.eps}}
                    \caption{Position detection study, single scatterer: ground-truth and reconstructed images by each algorithm.}
                    \label{fig:position:single:recons}
                \end{figure*}

@@

                \begin{figure*}[!htb]
                    \centering
                    \subfigure[Ground-Truth]{\includegraphics[height=0.5\columnwidth]{../experiments/position/multiple/figs/0.eps}\label{fig:position:multiple:ground_truth}}
                    \subfigure[OSM]{\includegraphics[height=0.5\columnwidth]{../experiments/position/multiple/figs/1.eps}}
                    \subfigure[BIM]{\includegraphics[height=0.5\columnwidth]{../experiments/position/multiple/figs/2.eps}} \\
                    \subfigure[CSI]{\includegraphics[height=0.5\columnwidth]{../experiments/position/multiple/figs/3.eps}}
                    \subfigure[SOM]{\includegraphics[height=0.5\columnwidth]{../experiments/position/multiple/figs/4.eps}}
                    \subfigure[CA]{\includegraphics[height=0.5\columnwidth]{../experiments/position/multiple/figs/5.eps}}
                    \caption{Position detection study, multiple scatterer: ground-truth and reconstructed images by each algorithm.}
                    \label{fig:position:multiple:recons}
                \end{figure*}

@@

            Since the repository provides three-dimensional phantoms while our scattering model is two-dimensional, a representative cross-section focusing on the breast interior was extracted, as shown in Fig. \ref{fig:breast:recons:ground_truth}. The resulting image contains 328 $\times$ 212 pixels with a spatial resolution of 0.5 mm $\times$ 0.5 mm per pixel.

            The phantom includes four tissue types: fatty, transitional, fibroconnective/glandular, and skin. The breast is immersed in a homogeneous background medium with relative permittivity $\epsilon_{rb} = 10$ and conductivity $\sigma = 0$ S/m. The operating frequency was set to 1 GHz, with electrical properties (both relative permittivity and conductivity) of breast tissues determined using the Debye model.

            The experimental configuration follows the previous studies: 80 incident sources, 80 measurement points, and 5\% noise level. Under these conditions, the DNL for this experiment is 0.013. Since the interior of the breast is a complex structure, keeping a low DNL value is an important strategy to facilitate the reconstruction. The resolution of the recovered image was set to 80 $\times$ 80 pixels.

            Since fibroglandular tissue represents the region of primary interest within the breast, an adjustment to the indicator calculation methodology was necessary. This modification was required because fatty tissue does not exhibit zero contrast (as it is not homogeneous like the immersion medium). Therefore, object classification based solely on an absolute contrast threshold greater than zero would be inadequate. Consequently, the threshold for object classification in the original image was set as 70\% of the value between the maximum and minimum contrast values. Through this approach, the fibroglandular tissue region was effectively isolated, allowing for relevant shape and position error calculations.

            The algorithm parameters were readjusted as follows:
            \begin{itemize}
                \item Linear Sampling Method (LSM):
                \begin{itemize}
                    \item Threshold: 0.95;
                    \item Regularization Method: Tikhonov with $\alpha = 1$.
                \end{itemize}
                \item Orthogonality Sampling Method (OSM):
                \begin{itemize}
                    \item Threshold: 0.9;
                \end{itemize}
                \item Born Iterative Method (BIM):
                \begin{itemize}
                    \item Regularization Method: Tikhonov with $\alpha = 10$
                    \item Stopping Criterion: 10 iterations.
                \end{itemize}
                \item Contrast Source Inversion (CSI):
                \begin{itemize}
                    \item Stopping Criterion: 1500 iterations.
                \end{itemize}
                \item Subspace Optimization Method (SOM):
                \begin{itemize}
                    \item Stopping Criterion: 100 iterations.
                    \item Eigenvalue Cutoff Index: 15.
                \end{itemize}
            \end{itemize}

            Fig. \ref{fig:breast:recons} presents the reconstruction results obtained by each algorithm. All methods successfully detected the fibroglandular tissue region, although the quantitative algorithms varied in their contrast estimations. CSI and SOM underestimated the contrast values, while BIM had the closest estimation. As expected, the algorithms struggled to reconstruct the thin skin layer. However, the boundary between the fatty tissue and the immersion medium is observable in several reconstructions.

            \begin{figure*}[!htb]
                \centering
                \subfigure[Ground-Truth]{\includegraphics[height=0.55\columnwidth]{../experiments/breast/figs/0.eps}\label{fig:breast:recons:ground_truth}}
                \subfigure[LSM]{\includegraphics[height=0.55\columnwidth]{../experiments/breast/figs/1.eps}}
                \subfigure[OSM]{\includegraphics[height=0.55\columnwidth]{../experiments/breast/figs/2.eps}} \\
                \subfigure[BIM]{\includegraphics[height=0.55\columnwidth]{../experiments/breast/figs/3.eps}} 
                \subfigure[CSI]{\includegraphics[height=0.55\columnwidth]{../experiments/breast/figs/4.eps}}
                \subfigure[SOM]{\includegraphics[height=0.55\columnwidth]{../experiments/breast/figs/5.eps}}
                % \subfigure[CA]{\includegraphics[height=0.4\columnwidth]{../experiments/breast/figs/6.eps}}
                \caption{Breast phantom study: ground-truth and reconstructed images by each algorithm.}
                \label{fig:breast:recons}
            \end{figure*}

            Table \ref{tab:breast:indicators} presents the shape and position error indicators for each algorithm. The shape error values exceed 57\% for all methods, indicating significant challenges in accurately reconstructing the glandular tissue structure. Since this tissue size is small compared to the image dimensions, variations in the size and shape of the tissue reconstruction can significantly impact the shape indicator. Regarding position detection, all algorithms achieved relatively low position errors (below 5\%), with SOM demonstrating the best performance at 1.6\%.

            \begin{table}[!htb]
                \centering
                \renewcommand{\arraystretch}{1.5}
                \caption{Breast phantom study: shape and position error indicators for each algorithm.}
                \label{tab:breast:indicators}
                \begin{tabular}{cccccc}
                    Method & LSM & OSM & BIM & CSI & SOM \\\hline %  & CA \\\hline
                    $\zeta_S$ (\%) & 83.6 & 78.6 & 57.2 & 81.4 & 118.8 \\ % & 86.5 \\
                    $\zeta_P$ (\%) & 2.2 & 4.3 & 3.1 & 3.5 & 1.6 %% & 4.2 \\
                \end{tabular}   
            \end{table}

@@
